Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Small Changes for Section 4.

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim \normal(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} CCT, which we adopt here to make our simulation results directly
comparable with theirs and more comparable with the rest of the literature. We
will use the same three functional forms for $\mu_j$ as CCT as well.

@@

To estimate the finite-sample coverage of our new bootstrap interval, we
simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT.

@@

Table~\ref{tbl:1} presents the results of these simulations. The rows labeled
``\bootuni'' show results for our proposed bootstrap interval; ``\cctuni'' and
``\ccttri'' show results for the analytically-corrected intervals. The first
three columns give the bias, SD, and RMSE of the \emph{bias corrected} point
estimators corresponding to each confidence interval.  As expected, these
estimators are close to unbiased, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

>>>>

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim \normal(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here to make our simulation results directly
comparable with theirs and the rest of the literature. We
will use the same three functional forms for $\mu_{j}$ as CCT as well.

@@

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT.

@@

Table~\ref{tbl:1} presents the results of these simulations. The rows labeled
``\bootuni'' show results for our proposed bootstrap interval; ``\cctuni'' and
``\ccttri'' show results for the analytically-corrected intervals. The first
three columns give the bias, standard deviation, and Root-MSE of the \emph{bias corrected} point
estimators corresponding to each confidence interval.  As expected, these
estimators are close to unbiased, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.
